---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rpc

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/rpc)](https://CRAN.R-project.org/package=rpc)
<!-- badges: end -->

Helper functions to work assist routine class scheduling tasks. 

## Installation

You can install the development version of rpc from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("laijasmine/rpc")
```

## Generate class information
Provide a start date and number of sessions to generate a draft schedule:
```{r example}
rpc::get_classes("2025-09-15", 9, TRUE)
```

Then use the generated class schedule and format it into a valid dataframe for Google Calendar
```{r}
class_schedule <- rpc::get_class_schedule(sheet = "2025 Fall")
calendar_df <- rpc::create_calendar_event(class_schedule)
calendar_df
```

Upload the saved csv file to Google:
```{r}
readr::write_csv(calendar_df, tempfile())
```
